Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

To validate the effectiveness of our proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196},
and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
for ease of comparison.
%
The setup is also consistent to standard DML~\cite{revisiting}.

Specifically, we train a ResNet-18~\cite{resnet} with the output dimension of
the last layer changed to $N=512$.
%
The margin $\gamma$ in triplet loss is set as $0.2$ by default.
%
The model is trained with Adam optimizer with learning rate $1.0\times 10^{-3}$
for $150$ epochs, with mini-batch size set as $112$.

@@

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard[], distance~\cite{distance}, and the hardest negative sampling
(\ie, the negative sample with the largest loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and destination
hardness, we adversarially train models on the CUB-200-2011 dataset with
every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.

>>>>

To validate the effectiveness of our proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
(CARS)~\cite{cars196}, and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
for ease of comparison.
%
The setup is also consistent to standard DML~\cite{revisiting}.

Specifically, we train a ResNet-18 (RN18)~\cite{resnet} with the output dimension of
the last layer changed to $N=512$.
%
The margin $\gamma$ in triplet loss is set as $0.2$ by default.
%
The model is trained with Adam optimizer with learning rate $1.0\times 10^{-3}$
for $150$ epochs, with mini-batch size set as $112$.

@@

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance}, and the hardest
negative sampling (\ie, the negative sample with the largest loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset with
every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.

### 2021-10-13 tab-desth.tex
tex

\caption{Combinations of Source/Destination Hardness.
	%
	Experiments are conducted on CUB Dataset.
	%
	Models on the diagonal do not use adversarial examples
	due to destination being unchanged.
	%
}
\label{tab:desth}

>>>>

	\caption{Combinations of Source \& Destination Hardness.
	%
	Experiments are conducted on CUB Dataset with RN18 model.
	%
	The last-epoch performance is reported instead of the peak performance.
	%
	Original data is used when the source and destination hardness are the
	same, as shown on the diagonal line of the table.
	%
}
	\label{tab:desth}
